---
title: "Assignment 8: K-Means Clustering"
author: "43141 (Sahil Naphade)"
date: "18/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installing required packages
```{r}
library(tidyverse)
library(cluster)
#install.packages("FactoMineR")
#install.packages("factoextra")
library(FactoMineR)
library(factoextra)
```

# Reading the dataset and removing null values
```{r}
df <- USArrests
df <- na.omit(df)
df <- scale(df)
head(df)
```

# Compute distance matrix between the rows of a data matrix. Visualizr the created distance matrix.
```{r}
distance <- get_dist(df)
fviz_dist(distance, gradient = list(low = "#00AFBB",mid = "white", 
                                    high = "#FC4E07"))
```
# Perform K-means clustering on the dataset with 3 clusters
```{r}
k3 <- kmeans(df, centers = 3, nstart = 25)
str(k3)
k3
```
# Visualize the created clusters
```{r}
fviz_cluster(k3, data = df)
```
# Intra-cluster variation (Known as total within-cluster variation/total 
# within-cluster sum of square)
# Implementation of Elbow method in R
```{r}
set.seed(123)
```
#Function to compute total within-cluster sum of square
```{r}
wss <- function(k){
  kmeans(df, k, nstart = 10)$tot.withinss
}
```
# compute and plot wss for k = 1 to k = 10
```{r}
k.values <- 1:10
```
# Extract wss for 2 - 15 clusters
```{r}
wss_values <- map_dbl(k.values, wss)
```
# Plot the elbow method (defined in fviz_nbclust)
```{r}
plot(k.values, wss_values, type = "b",
     pch = 19, frame = F, xlab = "Number of clusters K",
     ylab = "Total within-clusters sum of squares")
```
```{r}
set.seed(123)
fviz_nbclust(df, kmeans, method = "wss")
```

# Optimal number of clusters = 4, therefore, calc final result using k = 4
```{r}
set.seed(123)
final <- kmeans(df, 4, nstart = 25)
print(final)
```
```{r}
fviz_cluster(final, data = df)
```